---
title: "在R Markdown文档中使用中文"
author:
  - 谢益辉
  - 邱怡轩
  - 于淼
documentclass: ctexart
output:
  rticles::ctex:
    fig_caption: yes
    number_sections: yes
    toc: yes
classoption: "hyperref,"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Expression
Expressions are composed of objects and functions.

## Objects
An object is a "thing" that is represented by the computer. Examples of objects in R include numeric vectors, charater vectors, lists, and functions.

```{r}
# a list
list(c(1,2,3,4,5),"this is an object","this whole thing is a list")
```

## Symbols
Variable names in R are called symbols.

## Functions
A function is an object in R that takes some input objects(arguments) and returns an output object.Every operation in R is a function call.

## Special Values
* **NA** not available.
* **Inf & -Inf** positive and negative infinity.
* **NaN** not a number.
* **NULL** NULL is often used as an argument in functions to mean that no value was assigned to the argument.

## Coercion
When you call a function with an argument of the wrong type, R will try to coerce values to a different type so that the function will work.\
roughly logical < integer < numeric < complex < character < list\
You can inhibit this by using the AsIs function.

## the R Interpreter
Some functionality is implemented internally within the R system.\
Many functions use `.Internal` to call internal R \
e.g. `plot.xy`\
R includes a mechanism to difine functions that are implemented completely internally.\
You can identify these functions because the body of the function contains a call to the function `.Primitive`.

## Seeing how R works
By calling `quote()` we can see how this expression is parsed.\
```{r}
x=1
if (x>1) "orange" else "apple"
quote(if (x>1) "orange" else "apple")
lapply(as(quote(if (x>1) "orange" else "apple"),"list"),typeof)


as.list(quote(x[2]))
deparse(quote(`[`(x,2)))
```
 
 You might try using `quote`, `substitute`, `typeof`, `class`, and `methods` to see how the R interpreter parses expressions.