---
title: "R learing 2"
author: "Wang,Liuying"
date: "2016年10月8日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Constants
### Numeric Victors

```{r}
#hexadcimal
0x1
0xFFFF
#numeiric type
typeof(1)
typeof(1:5)
#limis of precision
(2^2013+1)==2^2013
2^2014
#complex values
#real_part+imaginary_parti
0+1i^2
sqrt(-1+0i)
exp(0+1i*pi)
#sqrt()function will return a value of the same type.
```

### Character Vectors
```{r}
identical("\"hello\"","hello")
identical('\'hello\'',"'hello'")
```

### Symbols
Not all words are valid as symbols.You can't use `If, else, repeat, while, function, for, in, next, break, TRUE, NULL, Inf, NaN, NA, NA_integer_, NA_complex_, NA_character_`, etc.

## Operations

```{r}
# addition
1+19
# multiplication
5*4
# modulus
41%%21
# exponents
2^1
# integer division
21%/%2
```

### Assignments
```{r}
v <- 1:8
dim(v) <- c(2,4)
v
z <- function(a,b,c){a^b/c}
formals(z) <- alist(a=1,b=2,c=3)#设置formal argument
z()
```

## Expressions
### Curly Braces `{}`
Often, curly baces are used to group a set of operations in the body of a function, and can also be used as expressions in other contexts. The contents of the curly braces are evaluated inside the current environment; note that a new environment is created by a function call **but not** by the use of curly braces.

## Control Structures
### Conditional Statements
The function `if` has the type `special`
```{r}
typeof(`if`)
```
In R, `if` conditional statements are not vector operations. If the conditon statement is a vector of more than one logical value, then only the first item will be used.\
If you would liake a vector operation, use the `ifelse` function instead.
```{r}
a <- rep("a",5)
b <- rep("b",5)
ifelse(c(T,T,F,F,T),a,b)
```
bonus:`switch`
```{r}
switcheroo.if.then <- function(x)
{
  switch(x,
         a="aligator",
         b="bear",
         c="camel",
         "moose")
}
switcheroo.if.then("a");switcheroo.if.then("f")
```

### Loop
There are three different looping constructs.\
1. Simplest is `repeat`.\
`repeat expression`, to wtop repeating use the keyword `break`.
```{r}
i <- 5
repeat{if(i>25) break else {print(i);i <- i+5}}
```
If you don't include a `break` command, the R code will be an infinite loop. This can be useful for creating an interactive application.\
2. Another useful construction is `while` loops.\
`while(condition*) expression`
```{r}
i <- 5
while(i<=25) {print(i);i <- i+5}
```
You can use `break` and `next` inside loops. The `break` is used to stop iterating through a loop. The `next` statement skips to the next loop iteration without evaluating the remaining expressions in the loop body.\
3. Finally, R provides `for` loops, which iterate through each item in a vector (or a list).\
`for (var in list) expression`
```{r}
for(i in seq(5,25,by=5)){print(i)}
```
#### Looping Extension
>I can't install this package now. This part is for referrence later.
Iterators can make code easier to parallelize. You'll need to install the iterators packages.\
`iter(obj, checkFunc=function(...) TRUE, recycle=FALSE,...)`
```{r}
library(iterators)
onetofive <- iter(1:5)
nextElem(onetofive)
nextElem(onetofive)
nextElem(onetofive)
```
A second extension is the foreach loop, available through the `foreach` package.
```{r}
library(foreach)
#foreach
sqrts.1to5 <- foreach(i=1:5) %do% sqrt(i)
#the %do% operator evaluates teh expression in serial, while the %dopar% can be used to evaluate expressions in  parallel.
```

##Accessing Data Structures
###Indexing 
Use single-bracket *[* to select a subset, and double-bracket *[[* to select a single element.\ 
If you select a subset of elements that corresponds to a matrix object; if you select a subset taht corresponds to only a vector. To disable this behavior, you can use the `drop=FALSE` option.
```{r}
a <- array(101:124,dim=c(2,3,4))
class(a[1,1,])
class(a[1,,])
class(a[1:2,1:2,1:2])
class(a[1,1,1,drop=F])
```
It is possible to replace elements in a vector, matrix, or array using the same notation.
```{r}
a[1:2,1:2,1] <- matrix(c(1001:1004),nrow=2,ncol=2)
```
###Indexing by logical vector
```{r}
v=100:119
v[rep(c(T,F),10)];v[c(T,F)]
v[(v==103)]
```
###Indexing by name
You can index a set of element by name using the *$* notation or the single-bracket notation *[*（Using double-bracket *[[* when selecting a single element. \
It is even possible to index by partial name using the `exact=FALSE`.
```{r}
dairy <- list(milk="1 gallon", butter="1 pound", eggs=12)
dairy$milk; dairy["milk"]; dairy[["milk"]]
dairy[["mil"]];dairy[["mil",exact=F]]
##升级版来了
fruit <- list(apples=6, oranges=3, bananas=10)
shopping.list <- list(dairy=dairy, fruit=fruit)
shopping.list
shopping.list[[c("dairy","milk")]];shopping.list[[c(1,2)]]
shopping.list$dairy$milk
```
