---
title: "Untitled"
author: "王柳盈"
date: "2017年7月18日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1.	(a) Simulate data: Y=a+b*X+e, where (a, b)=(1, 1), X~unif(-1, 1), and the random error e has a standard normal distribution. Set the sample size=100;
(b) For the MLE of b, construct the 95% confidence interval using the jackknife approach;
(c) For the MLE of b, construct the 95% confidence interval using the block jackknife approach with 20 blocks;
(c) Repeat (a) to (c) 100 times. Compare the empirical coverage rates with the target, and evaluate the performance of jackknife and block jackknife.

```{r}
#a
a=1;b=1;n=100
x <- runif(100,-1,1)
y <- a+b*x+rnorm(100)

#b
library(maxLik)
logLik <- function(par,x,y){  sum(dnorm(y,mean=par[1]+par[2]*x,sd=1,log = T))}
fit <- maxLik(logLik,x=x,y=y,start=c(0,0))
(hatb <- fit$estimate[2])


jackknife_single <- function(i,x,y,logLik)
{
  require(maxLik)
  fit <- maxLik(logLik,x=x[-i],y=y[-i],start=c(0,0))
  hatb <- fit$estimate[2]
  return(hatb)
}
jackknife_single(1,x,y,logLik)

jackknife <- function(x,y,logLik)
{
  index <- 1:length(x)
  sapply(index,jackknife_single,x,y,logLik)
}


jackknife_CI <- function(x,y,logLik,alpha)
{
  fit <- maxLik(logLik,x=x,y=y,start=c(0,0))
  hatb <- fit$estimate[2]
  b_jak <- jackknife(x,y,logLik)
  var_jak <- (n-1)/n*sum((b_jak-mean(b_jak))^2)
  CI <- c(hatb+qnorm(alpha/2)*sqrt(var_jak),hatb+qnorm(1-alpha/2)*sqrt(var_jak))
  return(CI)
}

jackknife_CI(x,y,logLik,0.05)

#c
m=20

jackknife_block <- function(x,y,logLik,m)
{
  index <- list();num_blo <- length(x)%/%m
  for (i in 1:m){index <- c(index,list(((i-1)*num_blo+1):(i*num_blo)))}
  sapply(index,jackknife_single,x,y,logLik)
}

jackknife_block(x,y,logLik,20)
jackknife_block_CI <- function(x,y,logLik,alpha,m)
{
  fit <- maxLik(logLik,x=x,y=y,start=c(0,0))
  hatb <- fit$estimate[2]
  b_jak <- jackknife_block(x,y,logLik,m)
  var_jak <- (length(x) %/% m)*(m-1)*sum((b_jak-mean(b_jak))^2)
  CI <- c(hatb+qnorm(alpha/2)*sqrt(var_jak),hatb+qnorm(1-alpha/2)*sqrt(var_jak))
  return(CI)
}
jackknife_block_CI(x,y,logLik,0.05,20)

#d
jackknife <- replicate(100,
                        {y <- a+b*x+rnorm(100);
                        jak <- jackknife_CI(x,y,logLik,0.05);
                        (b>jak[1]&b<jak[2])})
sum(jackknife)


jackknifeblock <- replicate(100,{y <- a+b*x+rnorm(100);
                          jak <- jackknife_block_CI(x,y,logLik,0.05,index);
                        (b>jak[1]&b<jak[2])})

sum(jackknifeblock)
```


2.	(a) Simulate data with a binary response Y that satisfies the logistic model: P(Y=1)=1/(1+exp(-b*X)). Set b=1 and X~unif(-2, 2). Set the sample size=200;
(b) For the MLE of b (estimated using the R function glm), construct the 95% confidence interval using the “n out of n” nonparametric bootstrap.
(c) For the MLE of b, constructed the 95% confidence interval using the “m out of n” nonparametric bootstrap with m=50; 
(c) Repeat (a) to (c) 100 times. Compare the empirical coverage rates with the target, and evaluate the performance of nonparametric bootstrap.

```{r}
#a
n=500;b <- 1;x <- runif(n,-2,2);prob.Y <- 1/(1+exp(-b*x))
mysample <- function(prob){sample(x = c(0,1),size = 1,prob = c(1-prob,prob))}
y <- sapply(prob.Y,mysample)
data <- data.frame(x=x,y=y)

#b
fit <- glm(y~x,family = binomial(link="logit"))
bhat <- fit$coefficients[2]

compute.bhat <- function(data,m)
{
  index <- sample(x=1:dim(data)[1],size=m,replace = T)
  fit <- glm(y~x,data=data,family = binomial(link="logit"),subset = index)
  return(fit$coefficients[2])
}

b.boot <- replicate(100,compute.bhat(data,dim(data)[1]))
b.boot.CI <- quantile(x = b.boot,probs = c(0.025,0.975))

as.numeric(b>b.boot.CI[1]&b<b.boot.CI[2])

#d
onetime <- function(n,b,x,m)
{
  prob.Y <- 1/(1+exp(-b*x))
  mysample <- function(prob){sample(x = c(0,1),size = 1,prob = c(1-prob,prob))}
  y <- sapply(prob.Y,mysample)
  data <- data.frame(x=x,y=y)
  compute.bhat <- function(data,m)
  {
    index <- sample(x=1:dim(data)[1],size=m,replace = T)
    fit <- glm(y~x,data=data,family = binomial(link="logit"),subset = index)
    return(fit$coefficients[2])
  }

  b.boot <- replicate(100,compute.bhat(data,dim(data)[1]))
  b.boot.CI <- quantile(x = b.boot,probs = c(0.025,0.975))

  as.numeric(b>b.boot.CI[1]&b<b.boot.CI[2])
}  


sum(replicate(100,onetime(n = 200,b = 1,x = x,m=200)))

sum(replicate(100,onetime(n = 200,b = 1,x = x,m=50)))
```

Submission requirements: the same as for quiz one.
