---
title: "Statistical computation"
author: "王柳盈"
date: "2017年7月16日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#####Problem 1
Generate 1000 random numbers with a normal distribution with (mean, variance)=(2, 2) and then truncated at 2(left) and 3 (right). 
Requirements: (a) use the rejection sampling approach; (b) the only existing random number generating function you can use is runif(); (c) Compute summary statistics (mean, sd, 25% and 75% percentiles).
```{r}
g <- function(x,mean,sigma2){1/sqrt(2*pi*sigma2)*exp(-(x-mean)^2/(2*sigma2))}

#truncated=c(2,3);n=1000
RejectSampling <- function(n,g,truncated,...)
{
    count=0;x=vector()
    while (count<n)
    {
      x0 <- runif(n = 1,min = truncated[1],max = truncated[2])
      y <- runif(n=1,min=0,max=1)
      if (y<g(x0,...)) {x=c(x,x0);count=count+1}
    }
    
  return(x)
}


y <- RejectSampling(1000,g=g,truncated=c(2,3),mean=2,sigma2=2)
summary(y)
```




#####Problem 2
Consider X with an exponential distribution and mean=2. Use the importance sampling Monte Carlo integration method to compute Pr(2<X<4).

```{r}
x <- rexp(1000,1/2)
(pro_2to4 <- sum(ifelse(x>2&x<4,1,0))/1000)
```

#####Problem 3
(a)	Simulate 200 data points from the model Y=a+b*log(X)+e, where the intercept a=1.2, the regression coefficient b=2.0, and the random error e has a standard normal distribution. X has a uniform distribution between 1 and 3.
(b)	Consider the following candidate models: (1) Y~a+b*X; (2) Y~a+b*X+b2X^2. Note that both models are mis-specified.
(c)	Use 5-fold CV to select the optimal model.
(d)	Repeat (a)-(c) 100 times, and summarize your results.

```{r}
n=200
x <- runif(n,1,3)
a <- 1.2;b <- 2.0
y <- a+b*log(x)+rnorm(200)

fit1 <- lm(y~x);summary(fit1)
fit2 <- lm(y~x+I(x^2));summary(fit2)

K <- 5

computeCV <- function(K,formula)
{  
  ytest <- vector()
  for (k in 1:K)
  {
    test <- ceiling(n/K*(k-1)+1):ceiling(n/K*k)
    trainset <- data.frame(x=x[-test],y=y[-test])
    fit <- lm(formula,trainset)
    ypre <- as.numeric(predict(fit,data.frame(x=x[test])))
    ytest <- c(ytest,ypre)
  }
  mean((y-ytest)^2)
}

model1.cv <- computeCV(5,y~x)
model2.cv <- computeCV(5,y~x+I(x^2))
model1.cv;model2.cv

ChooseModel <- function(K,formula1,formula2)
{
  x <- runif(n,1,3)
  a <- 1.2;b <- 2.0
  y <- a+b*log(x)+rnorm(200)
  model1.cv <- computeCV(K=K,formula = formula1)
  model2.cv <- computeCV(K=K,formula=formula2)
  if (model1.cv<model2.cv) return("model1")
  else return("model2")
}
finalresult <- replicate(100,ChooseModel(5,y~x,y~x+I(x^2)))
sum(finalresult=="model1")
```

